\documentclass[12pt,a4paper]{article}
\usepackage{times}
\usepackage{durhampaper}
\usepackage{harvard}
\usepackage{enumitem}


\usepackage{algorithm, algpseudocode}

\usepackage{booktabs}
\usepackage{longtable}

\usepackage{graphicx}
\usepackage{wrapfig}

\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

\citationmode{abbr}
\bibliographystyle{agsm}



\begin{document}
\begin{tabular}[t]{p{.30\textwidth}  p{.55\textwidth}  p{.20\textwidth}}
  \textbf{Harry Alexander Richards}  & & \textbf{06/05/2019} \\
  \textbf{Daniel Paulusma} & & \textbf{Deliverables} \\
  \textit{Durham University} & & 
\end{tabular}

\vspace{1cm}

\subsection*{Basic Objectives}
\begin{enumerate}[label = \textbf{B\arabic*}]
\itemsep0em
\item Design a tool in which one can input benchmark graphs in DIMACS standard format. \label{obj:B1}
\item Implement a simple greedy algorithm, such as first-fit.  \label{obj:B2}
\item Use heuristics to alter the order in which vertices are considered when performing the greedy algorithm and see how this impacts the colourings produced. \label{obj:B3}
\item Implement a number of other more advanced graph colouring heuristics that are more suited to specific graph classes. \label{obj:B4}
\item Implement a graph colouring checker, which verifies that colourings are valid. \label{obj:B5}
\end{enumerate}

\subsection*{Intermediate Objectives}
\begin{enumerate}[label = \textbf{I\arabic*}]
\itemsep0em
\item Develop a genetic algorithm that will be performed on the benchmark graphs. \label{obj:I1}
\item Develop a simulated annealing algorithm that will be performed on the benchmark graphs. \label{obj:I2}
\item Produce a hybrid algorithm that utilises aspects of both the genetic algorithm and simulated annealing. \label{obj:I5}
\item Alter the algorithms developed up to this point so to improve their performance on a number of special-case graph classes. \label{obj:I3}
\item Analyse the colourings yielded by the algorithms thus far and interpret how the algorithms exploit properties of particular graph classes. \label{obj:I4}

\end{enumerate}  

\subsection*{Advanced Objectives}
\begin{enumerate}[label = \textbf{A\arabic*}]
\itemsep0em
\item Produce a hybrid algorithm of genetic algorithm and tabu search. \label{obj:A3}
\item Handle large graphs with $100s - 1000s$ of vertices, and very dense graphs. \label{obj:A2}
\item Visualise the colouring process of the algorithms. \label{obj:A1}


\end{enumerate}



\end{document}
